---
title: "WSAP Analysis: Interpretation in Social Anxiety"
subtitle: "Replication of Beard & Amir (2009)"
author: "Eric Martz"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 6
)
```

# Configuration

**Note:** The paper (Beard & Amir 2009) used the **30th and 70th percentiles** to define groups:
- **SA group:** Top 30% of social anxiety scores (≥70th percentile)
- **NAC group:** Bottom 30% of social anxiety scores (≤30th percentile)  
- **Excluded:** Middle 40%

By default, this script automatically calculates these percentiles from your sample. You can optionally use fixed cutoffs instead.

```{r config}
# DATA SETTINGS
DATA_FOLDER <- "../data/"           # Folder with participant CSV files
WSAP_REFERENCE <- "WSAP.csv"        # Reference file with word-sentence pairs

# RT CLEANING (per paper)
RT_MIN <- 50                        # Minimum RT in ms
RT_MAX <- 2000                      # Maximum RT in ms

# GROUP ASSIGNMENT (per paper: top 30% vs bottom 30%)
USE_PERCENTILES <- TRUE             # TRUE = use 30th/70th percentiles from sample
                                    # FALSE = use fixed SPIN cutoffs below
SPIN_CUTOFF_HIGH <- 24              # Only used if USE_PERCENTILES = FALSE
SPIN_CUTOFF_LOW <- 12               # Only used if USE_PERCENTILES = FALSE
```

```{r packages}
library(tidyverse)
library(ez)
library(lsr)
library(knitr)
library(kableExtra)

theme_set(theme_minimal())
```

---

# Data Loading & Cleaning

## Load WSAP Reference

```{r load-reference}
wsap_reference <- read_csv(WSAP_REFERENCE, show_col_types = FALSE) %>%
  rename(
    set = Test,
    valence = `Trial type`,
    word = Word,
    sentence = Sentence,
    domain = Domain
  ) %>%
  mutate(
    valence = tolower(valence),
    valence = if_else(valence == "negative", "threat", "benign"),
    sentence_type = case_when(
      domain == "sad" ~ "social",
      domain == "gad" ~ "non_social",
      TRUE ~ NA_character_
    ),
    word = str_trim(word),
    sentence = str_trim(sentence)
  ) %>%
  select(set, word, sentence, valence, sentence_type)

cat("Loaded", nrow(wsap_reference), "word-sentence pairs\n")
cat("Sets:", paste(unique(wsap_reference$set), collapse = ", "), "\n")
cat("Valences:", paste(unique(wsap_reference$valence), collapse = ", "), "\n")
cat("Sentence types:", paste(unique(wsap_reference$sentence_type), collapse = ", "), "\n")
```

## Load Participant Data

```{r load-participant-data}
csv_files <- list.files(DATA_FOLDER, pattern = "\\.csv$", full.names = TRUE)

cat("Loading", length(csv_files), "participant file(s)\n")

df_list <- lapply(csv_files, function(file) {
  # Read with all columns as character first to avoid type conflicts
  df <- read_csv(file, show_col_types = FALSE, col_types = cols(.default = "c"))
  
  if (!"subject" %in% names(df)) {
    df$subject <- tools::file_path_sans_ext(basename(file))
  }
  return(df)
})

# Combine all files
raw_data <- bind_rows(df_list)

# Standardize column names (handle different versions)
raw_data <- raw_data %>%
  mutate(
    # Use judgment_rt if it exists, otherwise use rt
    judgment_rt = if_else(is.na(judgment_rt) & !is.na(rt), rt, judgment_rt),
    # Use response_key if it exists, otherwise use response
    response_key = if_else(is.na(response_key) & !is.na(response), response, response_key)
  )

# Convert key columns to correct types
raw_data <- raw_data %>%
  mutate(
    # Numeric conversions
    across(c(judgment_rt, spin_total, stai_state_total, stai_trait_total, 
             bdi_total, trial_index, time_elapsed), 
           ~suppressWarnings(as.numeric(.))),
    # Character conversions
    across(c(task, word, sentence, domain, response_key, subject), as.character)
  )

cat("Loaded data for", n_distinct(raw_data$subject), "subjects\n")

# Check for incomplete participants
wsap_counts <- raw_data %>%
  filter(task == "wsap", !is.na(judgment_rt)) %>%
  group_by(subject) %>%
  summarise(n_trials = n(), .groups = "drop")

if (any(wsap_counts$n_trials < 50)) {
  incomplete <- wsap_counts %>% filter(n_trials < 50)
  cat("\n⚠️ Warning: The following participants have incomplete data:\n")
  for (i in 1:nrow(incomplete)) {
    cat("  ", incomplete$subject[i], ": only", incomplete$n_trials[i], "WSAP trials\n")
  }
  cat("  These participants will be excluded from analysis.\n")
}
```

## Clean WSAP Trials

```{r clean-wsap-trials}
wsap_clean <- raw_data %>%
  # Filter to WSAP judgment trials only
  filter(task == "wsap", !is.na(judgment_rt)) %>%
  
  # Clean word and sentence for matching
  mutate(
    word = str_trim(word),
    sentence = str_trim(sentence)
  ) %>%
  
  # Merge with reference to get valence
  left_join(
    wsap_reference %>% select(word, sentence, valence, sentence_type),
    by = c("word", "sentence")
  ) %>%
  
  # Create key variables
  mutate(
    response_type = case_when(
      response_key == "1" ~ "endorsement",
      response_key == "3" ~ "rejection",
      TRUE ~ NA_character_
    ),
    endorsed = if_else(response_key == "1", 1, 0),
    rt_clean = case_when(
      judgment_rt >= RT_MIN & judgment_rt <= RT_MAX ~ judgment_rt,
      TRUE ~ NA_real_
    )
  ) %>%
  
  # Keep only valid trials and trial-level variables
  filter(!is.na(valence), !is.na(sentence_type), !is.na(response_type)) %>%
  
  # Select only trial-level columns (drop participant-level variables to avoid conflicts)
  select(subject, trial_index, word, sentence, domain, valence, sentence_type,
         response_type, endorsed, judgment_rt, rt_clean)

# Exclude participants with too few trials (< 50 suggests incomplete data)
valid_subjects <- wsap_clean %>%
  group_by(subject) %>%
  summarise(n_trials = n(), .groups = "drop") %>%
  filter(n_trials >= 50) %>%
  pull(subject)

wsap_clean <- wsap_clean %>%
  filter(subject %in% valid_subjects)

n_excluded_rt <- sum(is.na(wsap_clean$rt_clean))
pct_excluded_rt <- round(100 * n_excluded_rt / nrow(wsap_clean), 1)

cat("\nCleaned WSAP trials:", nrow(wsap_clean), "\n")
cat("RT outliers excluded:", n_excluded_rt, "(", pct_excluded_rt, "%)\n")
cat("Valid subjects in analysis:", n_distinct(wsap_clean$subject), "\n")

head(wsap_clean)
```

---

# Participant-Level Processing

## Extract Participant Info & Assign Groups

```{r participant-info}
participant_info <- raw_data %>%
  group_by(subject) %>%
  slice(1) %>%
  select(subject, set_assigned, spin_total, stai_state_total, 
         stai_trait_total, bdi_total, age, gender) %>%
  ungroup() %>%
  # Only keep participants with valid WSAP data
  filter(subject %in% valid_subjects)

cat("\n=== PARTICIPANTS ===\n")
cat("Total subjects with valid data:", n_distinct(participant_info$subject), "\n")

# Calculate group assignment
if (USE_PERCENTILES) {
  # Use 30th and 70th percentiles (per Beard & Amir 2009)
  percentile_30 <- quantile(participant_info$spin_total, 0.30, na.rm = TRUE)
  percentile_70 <- quantile(participant_info$spin_total, 0.70, na.rm = TRUE)
  
  participant_info <- participant_info %>%
    mutate(
      group = case_when(
        spin_total >= percentile_70 ~ "SA",   # Top 30%
        spin_total <= percentile_30 ~ "NAC",  # Bottom 30%
        TRUE ~ "exclude"                       # Middle 40%
      )
    )
  
  cat("\n=== GROUP ASSIGNMENT (PERCENTILE-BASED) ===\n")
  cat("Method: Top 30% vs Bottom 30% (per Beard & Amir 2009)\n")
  cat("30th percentile (NAC cutoff): SPIN ≤", percentile_30, "\n")
  cat("70th percentile (SA cutoff):  SPIN ≥", percentile_70, "\n\n")
  
} else {
  # Use fixed cutoffs
  participant_info <- participant_info %>%
    mutate(
      group = case_when(
        spin_total >= SPIN_CUTOFF_HIGH ~ "SA",
        spin_total <= SPIN_CUTOFF_LOW ~ "NAC",
        TRUE ~ "exclude"
      )
    )
  
  cat("\n=== GROUP ASSIGNMENT (FIXED CUTOFFS) ===\n")
  cat("SA (High Social Anxiety):  SPIN ≥", SPIN_CUTOFF_HIGH, "\n")
  cat("NAC (Low Social Anxiety):  SPIN ≤", SPIN_CUTOFF_LOW, "\n\n")
}

print(table(participant_info$group))

# Show SPIN distribution
cat("\nSPIN Score Distribution:\n")
cat("Range:", min(participant_info$spin_total, na.rm = TRUE), "-",
    max(participant_info$spin_total, na.rm = TRUE), "\n")
cat("Mean:", round(mean(participant_info$spin_total, na.rm = TRUE), 1), "\n")
cat("SD:", round(sd(participant_info$spin_total, na.rm = TRUE), 1), "\n")
```

## Calculate Endorsement Rates

```{r endorsement-rates}
endorsement_rates <- wsap_clean %>%
  group_by(subject, sentence_type, valence) %>%
  summarise(
    pct_endorsed = mean(endorsed, na.rm = TRUE) * 100,
    n_trials = n(),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from = c(sentence_type, valence),
    values_from = pct_endorsed,
    names_prefix = "pct_"
  )
```

## Calculate Reaction Times

```{r reaction-times}
rt_means <- wsap_clean %>%
  filter(!is.na(rt_clean)) %>%
  group_by(subject, sentence_type, valence, response_type) %>%
  summarise(
    mean_rt = mean(rt_clean, na.rm = TRUE),
    n_trials = n(),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from = c(sentence_type, valence, response_type),
    values_from = mean_rt,
    names_prefix = "rt_"
  )
```

## Calculate Bias Scores

```{r bias-scores}
bias_scores <- rt_means %>%
  mutate(
    # Threat bias = RT(reject threat) - RT(endorse threat)
    threat_bias_social = rt_social_threat_rejection - rt_social_threat_endorsement,
    benign_bias_social = rt_social_benign_endorsement - rt_social_benign_rejection,
    
    threat_bias_nonsocial = rt_non_social_threat_rejection - rt_non_social_threat_endorsement,
    benign_bias_nonsocial = rt_non_social_benign_endorsement - rt_non_social_benign_rejection
  ) %>%
  select(subject, contains("bias"))
```

## Combine All Participant Data

```{r combine-participant-data}
participant_data <- participant_info %>%
  left_join(endorsement_rates, by = "subject") %>%
  left_join(rt_means, by = "subject") %>%
  left_join(bias_scores, by = "subject")

# Filter to analysis groups only
analysis_data <- participant_data %>%
  filter(group %in% c("SA", "NAC"))

cat("\n=== ANALYSIS SAMPLE ===\n")
cat("Total participants:", nrow(analysis_data), "\n")
cat("SA group:", sum(analysis_data$group == "SA"), "\n")
cat("NAC group:", sum(analysis_data$group == "NAC"), "\n")
```

---

# Table 2: Descriptive Statistics

```{r table2}
table2 <- analysis_data %>%
  group_by(group) %>%
  summarise(
    n = n(),
    
    # Self-report indices (%)
    social_threat_M = mean(pct_social_threat, na.rm = TRUE),
    social_threat_SD = sd(pct_social_threat, na.rm = TRUE),
    social_benign_M = mean(pct_social_benign, na.rm = TRUE),
    social_benign_SD = sd(pct_social_benign, na.rm = TRUE),
    
    nonsocial_threat_M = mean(pct_non_social_threat, na.rm = TRUE),
    nonsocial_threat_SD = sd(pct_non_social_threat, na.rm = TRUE),
    nonsocial_benign_M = mean(pct_non_social_benign, na.rm = TRUE),
    nonsocial_benign_SD = sd(pct_non_social_benign, na.rm = TRUE),
    
    # RT indices (ms) - Social sentences
    rt_social_endorse_threat_M = mean(rt_social_threat_endorsement, na.rm = TRUE),
    rt_social_endorse_threat_SD = sd(rt_social_threat_endorsement, na.rm = TRUE),
    rt_social_endorse_benign_M = mean(rt_social_benign_endorsement, na.rm = TRUE),
    rt_social_endorse_benign_SD = sd(rt_social_benign_endorsement, na.rm = TRUE),
    rt_social_reject_threat_M = mean(rt_social_threat_rejection, na.rm = TRUE),
    rt_social_reject_threat_SD = sd(rt_social_threat_rejection, na.rm = TRUE),
    rt_social_reject_benign_M = mean(rt_social_benign_rejection, na.rm = TRUE),
    rt_social_reject_benign_SD = sd(rt_social_benign_rejection, na.rm = TRUE),
    
    # Bias scores
    threat_bias_M = mean(threat_bias_social, na.rm = TRUE),
    threat_bias_SD = sd(threat_bias_social, na.rm = TRUE),
    benign_bias_M = mean(benign_bias_social, na.rm = TRUE),
    benign_bias_SD = sd(benign_bias_social, na.rm = TRUE),
    
    # RT indices (ms) - Non-social sentences
    rt_nonsocial_endorse_threat_M = mean(rt_non_social_threat_endorsement, na.rm = TRUE),
    rt_nonsocial_endorse_threat_SD = sd(rt_non_social_threat_endorsement, na.rm = TRUE),
    rt_nonsocial_endorse_benign_M = mean(rt_non_social_benign_endorsement, na.rm = TRUE),
    rt_nonsocial_endorse_benign_SD = sd(rt_non_social_benign_endorsement, na.rm = TRUE),
    rt_nonsocial_reject_threat_M = mean(rt_non_social_threat_rejection, na.rm = TRUE),
    rt_nonsocial_reject_threat_SD = sd(rt_non_social_threat_rejection, na.rm = TRUE),
    rt_nonsocial_reject_benign_M = mean(rt_non_social_benign_rejection, na.rm = TRUE),
    rt_nonsocial_reject_benign_SD = sd(rt_non_social_benign_rejection, na.rm = TRUE),
    
    .groups = "drop"
  )

# Display Table 2
kable(table2, digits = 2, caption = "Table 2: WSAP Indices by Group") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), 
                full_width = FALSE, font_size = 11) %>%
  scroll_box(width = "100%")
```

---

# Mixed ANOVA Analyses

## Prepare Long Format Data

```{r prepare-anova-data}
anova_data_long <- wsap_clean %>%
  left_join(participant_info %>% select(subject, group, spin_total), by = "subject") %>%
  filter(group %in% c("SA", "NAC")) %>%
  select(subject, group, spin_total, sentence_type, valence, 
         response_type, rt_clean, endorsed, trial_index) %>%
  mutate(
    group = factor(group, levels = c("NAC", "SA")),
    sentence_type = factor(sentence_type, levels = c("social", "non_social")),
    valence = factor(valence, levels = c("benign", "threat")),
    response_type = factor(response_type, levels = c("endorsement", "rejection"))
  )

cat("ANOVA dataset:", nrow(anova_data_long), "trials\n")
cat("Participants:", n_distinct(anova_data_long$subject), "\n")
```

## Mixed ANOVA: Reaction Time

**Design:** Group (SA, NAC) × Valence (threat, benign) × Response Type (endorsement, rejection) × Sentence Type (social, non-social)

```{r anova-rt}
anova_rt <- ezANOVA(
  data = anova_data_long %>% filter(!is.na(rt_clean)),
  dv = rt_clean,
  wid = subject,
  within = .(valence, response_type, sentence_type),
  between = group,
  type = 3,
  detailed = TRUE
)

print(anova_rt)

# Save results
write_rds(anova_rt, "anova_rt_results.rds")
```

### Key Effects Interpretation

```{r rt-interpretation}
cat("\n=== KEY RT FINDINGS ===\n\n")

# Extract p-values for key effects
rt_anova_table <- anova_rt$ANOVA

# Main effect of Group
group_p <- rt_anova_table$p[rt_anova_table$Effect == "group"]
cat("Main effect of Group: p =", format.pval(group_p, digits = 3), "\n")

# Group × Valence × Response Type interaction (KEY finding)
interaction_idx <- which(str_detect(rt_anova_table$Effect, "group:valence:response_type"))
if(length(interaction_idx) > 0) {
  interaction_p <- rt_anova_table$p[interaction_idx[1]]
  cat("Group × Valence × Response Type: p =", format.pval(interaction_p, digits = 3), "\n")
}
```

## Mixed ANOVA: Endorsement Rates

**Design:** Group (SA, NAC) × Valence (threat, benign) × Sentence Type (social, non-social)

```{r anova-endorsement}
anova_endorsement <- ezANOVA(
  data = anova_data_long,
  dv = endorsed,
  wid = subject,
  within = .(valence, sentence_type),
  between = group,
  type = 3,
  detailed = TRUE
)

print(anova_endorsement)

# Save results
write_rds(anova_endorsement, "anova_endorsement_results.rds")
```

### Key Effects Interpretation

```{r endorsement-interpretation}
cat("\n=== KEY ENDORSEMENT FINDINGS ===\n\n")

# Extract p-values for key effects
endorse_anova_table <- anova_endorsement$ANOVA

# Main effect of Group
group_p <- endorse_anova_table$p[endorse_anova_table$Effect == "group"]
cat("Main effect of Group: p =", format.pval(group_p, digits = 3), "\n")

# Group × Valence interaction (KEY finding)
interaction_idx <- which(str_detect(endorse_anova_table$Effect, "group:valence"))
if(length(interaction_idx) > 0) {
  interaction_p <- endorse_anova_table$p[interaction_idx[1]]
  cat("Group × Valence: p =", format.pval(interaction_p, digits = 3), "\n")
}

# Group × Valence × Sentence Type
three_way_idx <- which(str_detect(endorse_anova_table$Effect, "group:valence:sentence_type"))
if(length(three_way_idx) > 0) {
  three_way_p <- endorse_anova_table$p[three_way_idx[1]]
  cat("Group × Valence × Sentence Type: p =", format.pval(three_way_p, digits = 3), "\n")
}
```

---

# Follow-Up Analyses

## Simple Effects: Group Differences by Valence

```{r simple-effects}
# Threat endorsement: SA vs NAC
threat_test <- t.test(
  pct_social_threat ~ group,
  data = analysis_data
)

# Benign endorsement: SA vs NAC
benign_test <- t.test(
  pct_social_benign ~ group,
  data = analysis_data
)

simple_effects <- tibble(
  Valence = c("Threat", "Benign"),
  `SA Mean` = c(
    mean(analysis_data$pct_social_threat[analysis_data$group == "SA"], na.rm = TRUE),
    mean(analysis_data$pct_social_benign[analysis_data$group == "SA"], na.rm = TRUE)
  ),
  `NAC Mean` = c(
    mean(analysis_data$pct_social_threat[analysis_data$group == "NAC"], na.rm = TRUE),
    mean(analysis_data$pct_social_benign[analysis_data$group == "NAC"], na.rm = TRUE)
  ),
  `t` = c(threat_test$statistic, benign_test$statistic),
  `df` = c(threat_test$parameter, benign_test$parameter),
  `p` = c(threat_test$p.value, benign_test$p.value)
)

kable(simple_effects, digits = 3, 
      caption = "Simple Effects: Group Differences by Valence (Social Sentences)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Within-Group Comparisons: Threat vs Benign

```{r within-group}
# SA group: threat vs benign
sa_data <- analysis_data %>% filter(group == "SA")
sa_within <- t.test(sa_data$pct_social_threat, sa_data$pct_social_benign, paired = TRUE)

# NAC group: threat vs benign
nac_data <- analysis_data %>% filter(group == "NAC")
nac_within <- t.test(nac_data$pct_social_threat, nac_data$pct_social_benign, paired = TRUE)

within_group <- tibble(
  Group = c("SA", "NAC"),
  `Threat Mean` = c(mean(sa_data$pct_social_threat, na.rm = TRUE),
                    mean(nac_data$pct_social_threat, na.rm = TRUE)),
  `Benign Mean` = c(mean(sa_data$pct_social_benign, na.rm = TRUE),
                    mean(nac_data$pct_social_benign, na.rm = TRUE)),
  `t` = c(sa_within$statistic, nac_within$statistic),
  `df` = c(sa_within$parameter, nac_within$parameter),
  `p` = c(sa_within$p.value, nac_within$p.value)
)

kable(within_group, digits = 3,
      caption = "Within-Group Comparisons: Threat vs Benign Endorsement") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Bias Score Comparisons

```{r bias-comparisons}
# Threat bias: SA vs NAC
threat_bias_test <- t.test(threat_bias_social ~ group, data = analysis_data)
threat_bias_d <- cohensD(threat_bias_social ~ group, data = analysis_data)

# Benign bias: SA vs NAC
benign_bias_test <- t.test(benign_bias_social ~ group, data = analysis_data)
benign_bias_d <- cohensD(benign_bias_social ~ group, data = analysis_data)

bias_comparisons <- tibble(
  `Bias Type` = c("Threat Bias", "Benign Bias"),
  `SA Mean` = c(
    mean(analysis_data$threat_bias_social[analysis_data$group == "SA"], na.rm = TRUE),
    mean(analysis_data$benign_bias_social[analysis_data$group == "SA"], na.rm = TRUE)
  ),
  `NAC Mean` = c(
    mean(analysis_data$threat_bias_social[analysis_data$group == "NAC"], na.rm = TRUE),
    mean(analysis_data$benign_bias_social[analysis_data$group == "NAC"], na.rm = TRUE)
  ),
  `t` = c(threat_bias_test$statistic, benign_bias_test$statistic),
  `df` = c(threat_bias_test$parameter, benign_bias_test$parameter),
  `p` = c(threat_bias_test$p.value, benign_bias_test$p.value),
  `Cohen's d` = c(threat_bias_d, benign_bias_d)
)

kable(bias_comparisons, digits = 3,
      caption = "Bias Score Comparisons: SA vs NAC") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Independence of Threat and Benign Biases

```{r bias-independence}
# Correlation between threat and benign bias scores
bias_cor <- cor.test(
  analysis_data$threat_bias_social,
  analysis_data$benign_bias_social,
  method = "pearson"
)

# Correlation between threat and benign endorsement rates
endorsement_cor <- cor.test(
  analysis_data$pct_social_threat,
  analysis_data$pct_social_benign,
  method = "pearson"
)

correlations <- tibble(
  Measure = c("Bias Scores (RT)", "Endorsement Rates"),
  r = c(bias_cor$estimate, endorsement_cor$estimate),
  `p` = c(bias_cor$p.value, endorsement_cor$p.value),
  `95% CI Lower` = c(bias_cor$conf.int[1], endorsement_cor$conf.int[1]),
  `95% CI Upper` = c(bias_cor$conf.int[2], endorsement_cor$conf.int[2])
)

kable(correlations, digits = 3,
      caption = "Independence of Threat and Benign Biases") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

cat("\nPaper reported:\n")
cat("  Bias scores: r = .20, p = .16 (not significant)\n")
cat("  Endorsement rates: r = -.25, p = .07 (not significant)\n")
```

## SPIN Correlations

```{r spin-correlations}
# SPIN × Threat bias
spin_threat_cor <- cor.test(analysis_data$spin_total, 
                            analysis_data$threat_bias_social)

# SPIN × Benign bias
spin_benign_cor <- cor.test(analysis_data$spin_total,
                            analysis_data$benign_bias_social)

# SPIN × Threat endorsement
spin_threat_endorse <- cor.test(analysis_data$spin_total,
                                analysis_data$pct_social_threat)

# SPIN × Benign endorsement
spin_benign_endorse <- cor.test(analysis_data$spin_total,
                                analysis_data$pct_social_benign)

spin_cors <- tibble(
  Measure = c("Threat Bias (RT)", "Benign Bias (RT)",
              "Threat Endorsement", "Benign Endorsement"),
  r = c(spin_threat_cor$estimate, spin_benign_cor$estimate,
        spin_threat_endorse$estimate, spin_benign_endorse$estimate),
  `p` = c(spin_threat_cor$p.value, spin_benign_cor$p.value,
          spin_threat_endorse$p.value, spin_benign_endorse$p.value)
)

kable(spin_cors, digits = 3,
      caption = "Correlations with SPIN (Social Anxiety Severity)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

---

# Summary

```{r summary}
cat("\n=== SAMPLE SUMMARY ===\n")
cat("Total participants:", nrow(analysis_data), "\n")

if (USE_PERCENTILES) {
  cat("SA group (top 30%, SPIN ≥", percentile_70, "):", sum(analysis_data$group == "SA"), "\n")
  cat("NAC group (bottom 30%, SPIN ≤", percentile_30, "):", sum(analysis_data$group == "NAC"), "\n\n")
} else {
  cat("SA group (SPIN ≥", SPIN_CUTOFF_HIGH, "):", sum(analysis_data$group == "SA"), "\n")
  cat("NAC group (SPIN ≤", SPIN_CUTOFF_LOW, "):", sum(analysis_data$group == "NAC"), "\n\n")
}

cat("=== KEY FINDINGS ===\n\n")

cat("1. Endorsement Rates:\n")
cat("   SA group: Threat =", round(mean(sa_data$pct_social_threat, na.rm = TRUE), 1), 
    "%, Benign =", round(mean(sa_data$pct_social_benign, na.rm = TRUE), 1), "%\n")
cat("   NAC group: Threat =", round(mean(nac_data$pct_social_threat, na.rm = TRUE), 1),
    "%, Benign =", round(mean(nac_data$pct_social_benign, na.rm = TRUE), 1), "%\n\n")

cat("2. Group Differences:\n")
cat("   Threat endorsement: t =", round(threat_test$statistic, 2),
    ", p =", format.pval(threat_test$p.value, digits = 3), "\n")
cat("   Benign endorsement: t =", round(benign_test$statistic, 2),
    ", p =", format.pval(benign_test$p.value, digits = 3), "\n\n")

cat("3. Bias Scores:\n")
cat("   Threat bias comparison: t =", round(threat_bias_test$statistic, 2),
    ", p =", format.pval(threat_bias_test$p.value, digits = 3),
    ", d =", round(threat_bias_d, 2), "\n")
cat("   Benign bias comparison: t =", round(benign_bias_test$statistic, 2),
    ", p =", format.pval(benign_bias_test$p.value, digits = 3),
    ", d =", round(benign_bias_d, 2), "\n\n")

cat("4. Independence of Biases:\n")
cat("   Bias scores correlation: r =", round(bias_cor$estimate, 3),
    ", p =", format.pval(bias_cor$p.value, digits = 3), "\n")
cat("   Endorsement correlation: r =", round(endorsement_cor$estimate, 3),
    ", p =", format.pval(endorsement_cor$p.value, digits = 3), "\n")
```

---

# Save Results

```{r save-results}
write_csv(table2, "table2_descriptives.csv")
write_csv(analysis_data, "participant_level_data.csv")
write_csv(anova_data_long, "anova_data_long.csv")
write_csv(simple_effects, "simple_effects.csv")
write_csv(within_group, "within_group_comparisons.csv")
write_csv(bias_comparisons, "bias_comparisons.csv")
write_csv(correlations, "bias_correlations.csv")
write_csv(spin_cors, "spin_correlations.csv")

cat("\n✓ All results saved\n")
```

---

# References

Beard, C., & Amir, N. (2009). Interpretation in Social Anxiety: When Meaning Precedes Ambiguity. *Cognitive Therapy and Research, 33*(4), 406-415. https://doi.org/10.1007/s10608-009-9235-0
