---
title: "WSAP Data Analysis: Replicating Beard & Amir (2009)"
author: "Eric Martz"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    code_folding: show
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 6
)
```

# Introduction

This analysis replicates the methodology from:

**Beard, C., & Amir, N. (2009).** Interpretation in Social Anxiety: When Meaning Precedes Ambiguity. *Cognitive Therapy and Research, 33*(4), 406-415.

## Study Overview

The Word Sentence Association Paradigm (WSAP) assesses interpretation bias by having participants judge whether words (suggesting negative or benign interpretations) are related to ambiguous sentences.

**Your Data Structure:**

- **110 unique sentence-interpretation pairs** (Test A and Test B combined)
- **220 total trials** (each sentence has both negative and benign interpretations)
- **Domains:** GAD (Generalized Anxiety) and SAD (Social Anxiety)
- **Interpretation types:** Negative vs. Benign

---

# Setup and Data Loading

## Load Required Packages

```{r load-packages}
# Install packages if needed (uncomment to run once)
# install.packages(c("tidyverse", "psych", "effsize", "ggpubr", "knitr", "kableExtra"))

library(tidyverse)    # Data manipulation and visualization
library(psych)        # Descriptive statistics and reliability
library(effsize)      # Effect size calculations
library(ggpubr)       # Publication-ready plots
library(knitr)        # Table formatting
library(kableExtra)   # Enhanced table styling

# Set theme for plots
theme_set(theme_bw(base_size = 12))
```

## Configuration

```{r config}

PARTICIPANT_DATA_FOLDER <- "../../Desktop/"

# Path to interpretation coding (already prepared for you!)
CODING_FILE <- "interpretation_coding_reference.csv"

# RT cleaning thresholds
RT_MIN <- 0     # milliseconds
RT_MAX <- 10000   # milliseconds

# Output directory
OUTPUT_DIR <- getwd()
```

## Load Interpretation Coding (Already Done For You! ✓)

```{r load-interpretation-coding}
# Load the interpretation coding from the reference file
# This was extracted from your WSAP.csv file
interpretation_coding <- read_csv(CODING_FILE, show_col_types = FALSE)

cat("✓ Loaded interpretation coding for", nrow(interpretation_coding), "trials\n\n")

# Display summary
cat("Breakdown by interpretation type:\n")
print(table(interpretation_coding$interpretation_type))

cat("\nBreakdown by domain:\n")
print(table(interpretation_coding$domain))

cat("\nBreakdown by test set:\n")
print(table(interpretation_coding$test_set))

# Display first few pairs
cat("\n", "="*80, "\n")
cat("SAMPLE WORD-SENTENCE PAIRS (First 10)\n")
cat("="*80, "\n")
kable(head(interpretation_coding, 10),
      caption = "First 10 Interpretation Pairs") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), 
                full_width = FALSE, font_size = 11)
```

---

# Data Preparation

## Load Participant Data

```{r load-participant-data}
cat("\n", "="*80, "\n")
cat("LOADING PARTICIPANT DATA\n")
cat("="*80, "\n")

# Check if we're loading from a folder or single file
if (exists("PARTICIPANT_DATA_FOLDER") && dir.exists(PARTICIPANT_DATA_FOLDER)) {
  # OPTION 2: Load all CSV files from folder
  cat("\n✓ Loading from FOLDER:", PARTICIPANT_DATA_FOLDER, "\n")
  
  # Get list of all CSV files in folder
  csv_files <- list.files(PARTICIPANT_DATA_FOLDER, 
                          pattern = "\\.csv$", 
                          full.names = TRUE,
                          ignore.case = TRUE)
  
  cat("  Found", length(csv_files), "CSV file(s)\n\n")
  
  if (length(csv_files) == 0) {
    stop("ERROR: No CSV files found in folder: ", PARTICIPANT_DATA_FOLDER)
  }
  
  # Display files found
  cat("Files to be loaded:\n")
  for (i in seq_along(csv_files)) {
    cat("  ", i, ". ", basename(csv_files[i]), "\n", sep = "")
  }
  cat("\n")
  
  # Read and combine all CSV files
  df_list <- list()
  for (i in seq_along(csv_files)) {
    cat("Reading file", i, "of", length(csv_files), ":", basename(csv_files[i]), "\n")
    
    # Read file
    temp_df <- read_csv(csv_files[i], show_col_types = FALSE)
    
    # If subject column doesn't exist, create one from filename
    if (!"subject" %in% names(temp_df)) {
      # Extract filename without extension as subject ID
      subject_id <- tools::file_path_sans_ext(basename(csv_files[i]))
      temp_df$subject <- subject_id
      cat("  → Added subject ID:", subject_id, "\n")
    }
    
    df_list[[i]] <- temp_df
  }
  
  # Combine all dataframes
  df_raw <- bind_rows(df_list)
  cat("\n✓ Successfully combined all files!\n")
  
} else if (exists("PARTICIPANT_DATA_FILE") && file.exists(PARTICIPANT_DATA_FILE)) {
  # OPTION 1: Load single CSV file
  cat("\n✓ Loading from FILE:", PARTICIPANT_DATA_FILE, "\n\n")
  df_raw <- read_csv(PARTICIPANT_DATA_FILE, show_col_types = FALSE)
  
} else {
  stop("\n\nERROR: Please specify either:\n",
       "  - PARTICIPANT_DATA_FOLDER (folder with CSV files), or\n",
       "  - PARTICIPANT_DATA_FILE (single CSV file)\n\n",
       "Update the path in the Configuration section above.")
}

# Display data structure
cat("\n=== DATA OVERVIEW ===\n")
cat("Total rows:", nrow(df_raw), "\n")
cat("Unique subjects:", n_distinct(df_raw$subject), "\n")
cat("\nSubjects found:\n")
print(sort(unique(df_raw$subject)))

cat("\n\nColumn names:\n")
print(names(df_raw))

# Display first few rows
cat("\nFirst 10 rows:\n")
kable(head(df_raw %>% select(any_of(c("subject", "word", "sentence", "response", "rt", "domain"))), 10),
      caption = "First 10 Rows of Participant Data") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## Clean and Merge Data

```{r clean-merge-data}
cat("\n=== PREPARING DATA ===\n")

# Convert response to binary
# Assuming: "1" or 1 = endorsed (YES/related), "3" or 3 = not endorsed (NO/not related)
df <- df_raw %>%
  mutate(
    endorsed = case_when(
      response == "1" | response == 1 ~ 1,
      response == "3" | response == 3 ~ 0,
      TRUE ~ NA_real_
    ),
    rt = as.numeric(rt),
    word = str_trim(word),
    sentence = str_trim(sentence)
  )

# Merge with interpretation coding
# Match on word and sentence
df <- df %>%
  left_join(
    interpretation_coding %>% 
      select(word, sentence, interpretation_type, domain_coded = domain),
    by = c("word", "sentence")
  )

# Check for uncoded trials
uncoded <- df %>%
  filter(is.na(interpretation_type)) %>%
  distinct(word, sentence)

if (nrow(uncoded) > 0) {
  cat("\n⚠️ WARNING:", nrow(uncoded), "uncoded word-sentence pairs found!\n")
  cat("\nUncoded pairs:\n")
  print(uncoded)
  cat("\n⚠️ These trials will be excluded from analysis.\n\n")
} else {
  cat("\n✓ All trials successfully matched with interpretation coding!\n\n")
}

# Remove uncoded trials
df <- df %>%
  filter(!is.na(interpretation_type))

# If domain not in participant data, use coded domain
if (!"domain" %in% names(df)) {
  df <- df %>% mutate(domain = domain_coded)
}

cat("Interpretation type distribution in participant data:\n")
print(table(df$interpretation_type))

cat("\nDomain distribution:\n")
print(table(df$domain))

cat("\nResponse distribution:\n")
print(table(df$response, useNA = "ifany"))
```

## Clean Reaction Time Data

```{r clean-rt}
cat("\n=== CLEANING REACTION TIME DATA ===\n")

initial_n <- nrow(df)

# Remove RTs outside acceptable range
df <- df %>%
  filter(rt >= RT_MIN & rt <= RT_MAX)

removed_n <- initial_n - nrow(df)
removed_pct <- (removed_n / initial_n) * 100

cat("Initial trials:", initial_n, "\n")
cat("Removed (< ", RT_MIN, "ms or > ", RT_MAX, "ms): ", 
    removed_n, " (", round(removed_pct, 1), "%)\n", sep = "")
cat("Retained trials:", nrow(df), "\n")
```

---

# Calculate Subject-Level Scores

```{r calculate-scores}
cat("\n=== CALCULATING SUBJECT-LEVEL SCORES ===\n")

# Calculate scores for each participant
subject_scores <- df %>%
  group_by(subject) %>%
  summarise(
    n_trials = n(),
    n_negative = sum(interpretation_type == "negative"),
    n_benign = sum(interpretation_type == "benign"),
    
    # Endorsement rates
    negative_endorsement = mean(endorsed[interpretation_type == "negative"], na.rm = TRUE),
    benign_endorsement = mean(endorsed[interpretation_type == "benign"], na.rm = TRUE),
    endorsement_bias = negative_endorsement - benign_endorsement,
    
    # RT for endorsed trials only
    negative_rt = mean(rt[interpretation_type == "negative" & endorsed == 1], na.rm = TRUE),
    benign_rt = mean(rt[interpretation_type == "benign" & endorsed == 1], na.rm = TRUE),
    rt_bias = negative_rt - benign_rt,
    
    # Count endorsed trials
    n_negative_endorsed = sum(interpretation_type == "negative" & endorsed == 1),
    n_benign_endorsed = sum(interpretation_type == "benign" & endorsed == 1),
    
    .groups = "drop"
  )

cat("Calculated scores for", nrow(subject_scores), "participants\n\n")

# Display subject scores
kable(subject_scores, 
      digits = 3,
      caption = "Subject-Level Bias Scores") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), 
                full_width = FALSE,
                font_size = 11) %>%
  scroll_box(width = "100%", height = "400px")

# Descriptive statistics
cat("\n=== DESCRIPTIVE STATISTICS ===\n")
desc_stats <- describe(subject_scores %>% 
           select(negative_endorsement, benign_endorsement, endorsement_bias,
                  negative_rt, benign_rt, rt_bias))

kable(desc_stats %>% 
        select(mean, sd, min, max, se), 
      digits = 3, 
      caption = "Summary Statistics") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

---

# Statistical Analyses

## 1. Endorsement Rate Analysis

### Paired t-test: Negative vs. Benign Endorsement

```{r endorsement-ttest}
cat("\n=== ENDORSEMENT RATE COMPARISON ===\n")
cat("Comparing: Negative vs. Benign Interpretation Endorsement\n\n")

# Paired t-test
endorsement_test <- t.test(
  subject_scores$negative_endorsement,
  subject_scores$benign_endorsement,
  paired = TRUE
)

# Calculate Cohen's d for paired samples
endorsement_diff <- subject_scores$negative_endorsement - subject_scores$benign_endorsement
cohens_d_endorse <- mean(endorsement_diff, na.rm = TRUE) / sd(endorsement_diff, na.rm = TRUE)

# Display results
cat("Negative endorsement: M =", round(mean(subject_scores$negative_endorsement, na.rm = TRUE), 3),
    ", SD =", round(sd(subject_scores$negative_endorsement, na.rm = TRUE), 3), "\n")
cat("Benign endorsement:   M =", round(mean(subject_scores$benign_endorsement, na.rm = TRUE), 3),
    ", SD =", round(sd(subject_scores$benign_endorsement, na.rm = TRUE), 3), "\n\n")

cat("Paired t-test results:\n")
cat("t(", endorsement_test$parameter, ") = ", round(endorsement_test$statistic, 3),
    ", p = ", format.pval(endorsement_test$p.value, digits = 4),
    ", Cohen's d = ", round(cohens_d_endorse, 3), "\n", sep = "")

if (endorsement_test$p.value < 0.05) {
  direction <- ifelse(mean(subject_scores$negative_endorsement) > mean(subject_scores$benign_endorsement),
                     "HIGHER", "LOWER")
  cat("\n✓ SIGNIFICANT: Negative endorsement is", direction, "than benign (p < .05)\n")
  cat("   Interpretation: ", 
      ifelse(direction == "HIGHER", 
             "Participants showed bias toward NEGATIVE interpretations",
             "Participants showed bias toward BENIGN interpretations"), "\n")
} else {
  cat("\n✗ Not significant (p ≥ .05)\n")
  cat("   No significant interpretation bias detected.\n")
}

# Effect size interpretation
cat("\nEffect size interpretation (Cohen's d = ", round(cohens_d_endorse, 3), "):\n", sep = "")
if (abs(cohens_d_endorse) < 0.2) {
  cat("   Negligible effect\n")
} else if (abs(cohens_d_endorse) < 0.5) {
  cat("   SMALL effect\n")
} else if (abs(cohens_d_endorse) < 0.8) {
  cat("   MEDIUM effect\n")
} else {
  cat("   LARGE effect\n")
}
```

## 2. Response Time Analysis (Endorsed Trials Only)

### Paired t-test: Negative vs. Benign RT

```{r rt-ttest}
cat("\n=== RESPONSE TIME COMPARISON (Endorsed Trials) ===\n")

# Remove participants with missing RT data
rt_complete <- subject_scores %>%
  filter(!is.na(negative_rt) & !is.na(benign_rt))

cat("Participants with complete RT data:", nrow(rt_complete), "\n\n")

if (nrow(rt_complete) > 1) {
  # Paired t-test
  rt_test <- t.test(
    rt_complete$negative_rt,
    rt_complete$benign_rt,
    paired = TRUE
  )
  
  # Calculate Cohen's d
  rt_diff <- rt_complete$negative_rt - rt_complete$benign_rt
  cohens_d_rt <- mean(rt_diff, na.rm = TRUE) / sd(rt_diff, na.rm = TRUE)
  
  # Display results
  cat("Negative RT: M =", round(mean(rt_complete$negative_rt, na.rm = TRUE), 1), "ms",
      ", SD =", round(sd(rt_complete$negative_rt, na.rm = TRUE), 1), "ms\n")
  cat("Benign RT:   M =", round(mean(rt_complete$benign_rt, na.rm = TRUE), 1), "ms",
      ", SD =", round(sd(rt_complete$benign_rt, na.rm = TRUE), 1), "ms\n\n")
  
  cat("Paired t-test results:\n")
  cat("t(", rt_test$parameter, ") = ", round(rt_test$statistic, 3),
      ", p = ", format.pval(rt_test$p.value, digits = 4),
      ", Cohen's d = ", round(cohens_d_rt, 3), "\n", sep = "")
  
  if (rt_test$p.value < 0.05) {
    direction <- ifelse(mean(rt_complete$negative_rt) < mean(rt_complete$benign_rt),
                       "FASTER", "SLOWER")
    cat("\n✓ SIGNIFICANT: Negative RT is", direction, "than benign (p < .05)\n")
    cat("   Interpretation: ",
        ifelse(direction == "FASTER",
               "Negative interpretations accessed more AUTOMATICALLY",
               "Negative interpretations processed more EFFORTFULLY"), "\n")
  } else {
    cat("\n✗ Not significant (p ≥ .05)\n")
    cat("   No significant RT difference.\n")
  }
  
  # Effect size interpretation
  cat("\nEffect size interpretation (Cohen's d = ", round(cohens_d_rt, 3), "):\n", sep = "")
  if (abs(cohens_d_rt) < 0.2) {
    cat("   Negligible effect\n")
  } else if (abs(cohens_d_rt) < 0.5) {
    cat("   SMALL effect\n")
  } else if (abs(cohens_d_rt) < 0.8) {
    cat("   MEDIUM effect\n")
  } else {
    cat("   LARGE effect\n")
  }
} else {
  cat("⚠️ Insufficient data for RT analysis (need at least 2 participants)\n")
}
```

## 3. Endorsement Bias Score (One-Sample t-test vs. Zero)

```{r bias-onesample}
cat("\n=== ENDORSEMENT BIAS SCORE (Test Against Zero) ===\n")

# One-sample t-test against zero
bias_test <- t.test(subject_scores$endorsement_bias, mu = 0)

# Cohen's d against zero
cohens_d_bias <- mean(subject_scores$endorsement_bias, na.rm = TRUE) / 
                 sd(subject_scores$endorsement_bias, na.rm = TRUE)

cat("Endorsement bias: M =", round(mean(subject_scores$endorsement_bias, na.rm = TRUE), 3),
    ", SD =", round(sd(subject_scores$endorsement_bias, na.rm = TRUE), 3), "\n")
cat("(Bias = Negative endorsement - Benign endorsement)\n\n")

cat("One-sample t-test (vs. 0):\n")
cat("t(", bias_test$parameter, ") = ", round(bias_test$statistic, 3),
    ", p = ", format.pval(bias_test$p.value, digits = 4),
    ", Cohen's d = ", round(cohens_d_bias, 3), "\n", sep = "")

if (bias_test$p.value < 0.05) {
  direction <- ifelse(mean(subject_scores$endorsement_bias) > 0, "POSITIVE", "NEGATIVE")
  cat("\n✓ SIGNIFICANT", direction, "bias (p < .05)\n")
  cat("   Interpretation: Participants show ",
      ifelse(direction == "POSITIVE",
             "systematic bias toward NEGATIVE interpretations",
             "systematic bias toward BENIGN interpretations"), "\n", sep = "")
} else {
  cat("\n✗ Not significant (p ≥ .05)\n")
  cat("   Bias score not significantly different from zero.\n")
}
```

## 4. Analysis by Domain

```{r domain-analysis}
cat("\n=== ANALYSIS BY ANXIETY DOMAIN ===\n")

# Calculate domain-specific bias
domain_scores <- df %>%
  group_by(subject, domain) %>%
  summarise(
    negative_endorsement = mean(endorsed[interpretation_type == "negative"], na.rm = TRUE),
    benign_endorsement = mean(endorsed[interpretation_type == "benign"], na.rm = TRUE),
    endorsement_bias = negative_endorsement - benign_endorsement,
    .groups = "drop"
  )

# Descriptive statistics by domain
domain_summary <- domain_scores %>%
  group_by(domain) %>%
  summarise(
    n = n(),
    mean_bias = mean(endorsement_bias, na.rm = TRUE),
    sd_bias = sd(endorsement_bias, na.rm = TRUE),
    se_bias = sd_bias / sqrt(n),
    .groups = "drop"
  )

cat("\nEndorsement Bias by Domain:\n")
kable(domain_summary, digits = 3,
      col.names = c("Domain", "N", "Mean Bias", "SD", "SE"),
      caption = "Endorsement Bias by Anxiety Domain") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Test if bias differs between domains (if both domains present)
if (n_distinct(domain_scores$domain) == 2) {
  # Reshape for paired t-test
  domain_wide <- domain_scores %>%
    pivot_wider(names_from = domain, 
                values_from = endorsement_bias,
                names_prefix = "bias_")
  
  # Check if we have paired data
  domain_cols <- grep("bias_", names(domain_wide), value = TRUE)
  
  if (length(domain_cols) == 2 && sum(complete.cases(domain_wide[domain_cols])) > 1) {
    domain_test <- t.test(domain_wide[[domain_cols[1]]], 
                          domain_wide[[domain_cols[2]]], 
                          paired = TRUE)
    
    cat("\n\nPaired t-test: GAD vs. SAD domain bias\n")
    cat("t(", domain_test$parameter, ") = ", round(domain_test$statistic, 3),
        ", p = ", format.pval(domain_test$p.value, digits = 4), "\n", sep = "")
    
    if (domain_test$p.value < 0.05) {
      cat("✓ Significant difference between domains (p < .05)\n")
    } else {
      cat("✗ No significant difference between domains (p ≥ .05)\n")
    }
  }
}
```

---

# Visualizations

## Figure 1: Endorsement Rates

```{r fig-endorsement, fig.width=12, fig.height=6}
# Prepare data for plotting
endorse_plot_data <- subject_scores %>%
  select(subject, negative_endorsement, benign_endorsement) %>%
  pivot_longer(cols = c(negative_endorsement, benign_endorsement),
               names_to = "interpretation_type",
               values_to = "endorsement_rate") %>%
  mutate(interpretation_type = factor(interpretation_type,
                                     levels = c("negative_endorsement", "benign_endorsement"),
                                     labels = c("Negative", "Benign")))

# Plot 1: Mean endorsement rates with error bars
p1 <- endorse_plot_data %>%
  group_by(interpretation_type) %>%
  summarise(
    mean = mean(endorsement_rate, na.rm = TRUE),
    se = sd(endorsement_rate, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = interpretation_type, y = mean, fill = interpretation_type)) +
  geom_bar(stat = "identity", width = 0.6, color = "black", alpha = 0.7) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.2, size = 1) +
  geom_text(aes(label = sprintf("%.3f", mean)), 
            vjust = -1.5, size = 5, fontface = "bold") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "gray40", size = 0.8) +
  scale_fill_manual(values = c("Negative" = "#d62728", "Benign" = "#2ca02c")) +
  labs(title = "Mean Endorsement Rates",
       subtitle = "Error bars show ±1 SE",
       x = "Interpretation Type",
       y = "Endorsement Rate") +
  ylim(0, 1) +
  theme_bw(base_size = 14) +
  theme(legend.position = "none",
        plot.title = element_text(face = "bold", size = 16),
        axis.title = element_text(face = "bold"))

# Plot 2: Distribution of bias scores
p2 <- ggplot(subject_scores, aes(x = endorsement_bias)) +
  geom_histogram(bins = 15, fill = "steelblue", color = "black", alpha = 0.7) +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", size = 1) +
  geom_vline(xintercept = mean(subject_scores$endorsement_bias, na.rm = TRUE),
             color = "darkblue", linetype = "solid", size = 1.2) +
  annotate("text", 
           x = mean(subject_scores$endorsement_bias, na.rm = TRUE),
           y = Inf,
           label = sprintf("Mean = %.3f", mean(subject_scores$endorsement_bias, na.rm = TRUE)),
           vjust = 2, hjust = ifelse(mean(subject_scores$endorsement_bias) > 0, -0.1, 1.1),
           size = 4.5, fontface = "bold") +
  labs(title = "Distribution of Endorsement Bias Scores",
       subtitle = "Negative - Benign",
       x = "Endorsement Bias Score",
       y = "Frequency") +
  theme_bw(base_size = 14) +
  theme(plot.title = element_text(face = "bold", size = 16),
        axis.title = element_text(face = "bold"))

# Combine plots
ggarrange(p1, p2, ncol = 2, labels = c("A", "B"))
```

## Figure 2: Response Times

```{r fig-rt, fig.width=12, fig.height=6}
# Prepare data for RT plotting
rt_plot_data <- subject_scores %>%
  filter(!is.na(negative_rt) & !is.na(benign_rt)) %>%
  select(subject, negative_rt, benign_rt) %>%
  pivot_longer(cols = c(negative_rt, benign_rt),
               names_to = "interpretation_type",
               values_to = "rt") %>%
  mutate(interpretation_type = factor(interpretation_type,
                                     levels = c("negative_rt", "benign_rt"),
                                     labels = c("Negative", "Benign")))

if (nrow(rt_plot_data) > 0) {
  # Plot 1: Mean RTs with error bars
  p3 <- rt_plot_data %>%
    group_by(interpretation_type) %>%
    summarise(
      mean = mean(rt, na.rm = TRUE),
      se = sd(rt, na.rm = TRUE) / sqrt(n()),
      .groups = "drop"
    ) %>%
    ggplot(aes(x = interpretation_type, y = mean, fill = interpretation_type)) +
    geom_bar(stat = "identity", width = 0.6, color = "black", alpha = 0.7) +
    geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.2, size = 1) +
    geom_text(aes(label = sprintf("%.0f", mean)), 
              vjust = -1.5, size = 5, fontface = "bold") +
    scale_fill_manual(values = c("Negative" = "#d62728", "Benign" = "#2ca02c")) +
    labs(title = "Mean Response Times (Endorsed Trials)",
         subtitle = "Error bars show ±1 SE",
         x = "Interpretation Type",
         y = "Response Time (ms)") +
    theme_bw(base_size = 14) +
    theme(legend.position = "none",
          plot.title = element_text(face = "bold", size = 16),
          axis.title = element_text(face = "bold"))
  
  # Plot 2: RT bias distribution
  p4 <- subject_scores %>%
    filter(!is.na(rt_bias)) %>%
    ggplot(aes(x = rt_bias)) +
    geom_histogram(bins = 15, fill = "coral", color = "black", alpha = 0.7) +
    geom_vline(xintercept = 0, color = "red", linetype = "dashed", size = 1) +
    geom_vline(xintercept = mean(subject_scores$rt_bias, na.rm = TRUE),
               color = "darkred", linetype = "solid", size = 1.2) +
    annotate("text", 
             x = mean(subject_scores$rt_bias, na.rm = TRUE),
             y = Inf,
             label = sprintf("Mean = %.1f ms", mean(subject_scores$rt_bias, na.rm = TRUE)),
             vjust = 2, hjust = ifelse(mean(subject_scores$rt_bias) > 0, -0.1, 1.1),
             size = 4.5, fontface = "bold") +
    labs(title = "Distribution of RT Bias Scores",
         subtitle = "Negative - Benign (ms)",
         x = "RT Bias Score (ms)",
         y = "Frequency") +
    theme_bw(base_size = 14) +
    theme(plot.title = element_text(face = "bold", size = 16),
          axis.title = element_text(face = "bold"))
  
  # Combine plots
  ggarrange(p3, p4, ncol = 2, labels = c("A", "B"))
} else {
  cat("⚠️ No RT data available for plotting\n")
}
```

## Figure 3: Domain-Specific Bias

```{r fig-domain, fig.width=10, fig.height=6}
if (n_distinct(domain_scores$domain) > 1) {
  ggplot(domain_scores, aes(x = domain, y = endorsement_bias, fill = domain)) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA) +
    geom_jitter(width = 0.2, alpha = 0.5, size = 2) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
    stat_summary(fun = mean, geom = "point", shape = 23, size = 4, 
                 fill = "white", color = "black") +
    scale_fill_brewer(palette = "Set2") +
    labs(title = "Endorsement Bias by Anxiety Domain",
         subtitle = "Diamond = mean, Box = median/IQR, Points = individual participants",
         x = "Anxiety Domain",
         y = "Endorsement Bias Score") +
    theme_bw(base_size = 14) +
    theme(legend.position = "none",
          plot.title = element_text(face = "bold", size = 16),
          axis.title = element_text(face = "bold"))
}
```

## Figure 4: Correlation Between Bias Scores

```{r fig-correlation, fig.width=8, fig.height=8}
if (nrow(subject_scores) > 5) {
  # Calculate correlation
  corr_data <- subject_scores %>%
    filter(!is.na(endorsement_bias) & !is.na(rt_bias))
  
  if (nrow(corr_data) > 2) {
    corr_test <- cor.test(corr_data$endorsement_bias, corr_data$rt_bias)
    
    # Create scatter plot
    ggplot(corr_data, aes(x = endorsement_bias, y = rt_bias)) +
      geom_point(size = 4, alpha = 0.6, color = "purple") +
      geom_smooth(method = "lm", se = TRUE, color = "red", fill = "pink", alpha = 0.2) +
      geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
      geom_vline(xintercept = 0, linetype = "dashed", color = "gray40") +
      annotate("text", x = -Inf, y = Inf,
               label = sprintf("r = %.3f\np = %.4f", 
                             corr_test$estimate, corr_test$p.value),
               hjust = -0.1, vjust = 2, size = 5.5, fontface = "bold",
               color = ifelse(corr_test$p.value < 0.05, "darkgreen", "black")) +
      labs(title = "Relationship Between Endorsement and RT Bias",
           subtitle = "Each point represents one participant",
           x = "Endorsement Bias Score",
           y = "RT Bias Score (ms)") +
      theme_bw(base_size = 14) +
      theme(plot.title = element_text(face = "bold", size = 16),
            axis.title = element_text(face = "bold"))
  }
}
```

---

# Summary of Results

## Key Findings Table

```{r summary-table}
# Create summary results table
summary_results <- tibble(
  Measure = c("Negative Endorsement", "Benign Endorsement", "Endorsement Bias",
              "Negative RT (endorsed)", "Benign RT (endorsed)", "RT Bias"),
  Mean = c(
    mean(subject_scores$negative_endorsement, na.rm = TRUE),
    mean(subject_scores$benign_endorsement, na.rm = TRUE),
    mean(subject_scores$endorsement_bias, na.rm = TRUE),
    mean(subject_scores$negative_rt, na.rm = TRUE),
    mean(subject_scores$benign_rt, na.rm = TRUE),
    mean(subject_scores$rt_bias, na.rm = TRUE)
  ),
  SD = c(
    sd(subject_scores$negative_endorsement, na.rm = TRUE),
    sd(subject_scores$benign_endorsement, na.rm = TRUE),
    sd(subject_scores$endorsement_bias, na.rm = TRUE),
    sd(subject_scores$negative_rt, na.rm = TRUE),
    sd(subject_scores$benign_rt, na.rm = TRUE),
    sd(subject_scores$rt_bias, na.rm = TRUE)
  ),
  Min = c(
    min(subject_scores$negative_endorsement, na.rm = TRUE),
    min(subject_scores$benign_endorsement, na.rm = TRUE),
    min(subject_scores$endorsement_bias, na.rm = TRUE),
    min(subject_scores$negative_rt, na.rm = TRUE),
    min(subject_scores$benign_rt, na.rm = TRUE),
    min(subject_scores$rt_bias, na.rm = TRUE)
  ),
  Max = c(
    max(subject_scores$negative_endorsement, na.rm = TRUE),
    max(subject_scores$benign_endorsement, na.rm = TRUE),
    max(subject_scores$endorsement_bias, na.rm = TRUE),
    max(subject_scores$negative_rt, na.rm = TRUE),
    max(subject_scores$benign_rt, na.rm = TRUE),
    max(subject_scores$rt_bias, na.rm = TRUE)
  )
)

kable(summary_results, digits = 3, caption = "Summary of All Measures") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## Interpretation

**Sample:** N = `r nrow(subject_scores)` participants

**Main Findings:**

1. **Endorsement Bias:** `r if(exists("endorsement_test")) { if(endorsement_test$p.value < 0.05) paste0("Participants showed **significant** interpretation bias (p = ", format.pval(endorsement_test$p.value, digits = 3), ", d = ", round(cohens_d_endorse, 2), "), endorsing negative interpretations ", ifelse(mean(subject_scores$negative_endorsement) > mean(subject_scores$benign_endorsement), "MORE", "LESS"), " than benign interpretations.") else "No significant difference in endorsement between negative and benign interpretations." } else "Analysis pending."`

2. **Response Time:** `r if(exists("rt_test") && nrow(rt_complete) > 1) { if(rt_test$p.value < 0.05) paste0("**Significant** RT difference (p = ", format.pval(rt_test$p.value, digits = 3), ", d = ", round(cohens_d_rt, 2), "). Negative interpretations were endorsed ", ifelse(mean(rt_complete$negative_rt) < mean(rt_complete$benign_rt), "FASTER", "SLOWER"), " than benign.") else "No significant RT difference." } else "Insufficient data for RT analysis."`

3. **Clinical Significance:** Effect sizes are interpreted using Cohen's guidelines: d = 0.2 (small), 0.5 (medium), 0.8 (large).

---

# Save Results

```{r save-results}
# Save subject scores to CSV
write_csv(subject_scores, file.path(OUTPUT_DIR, "wsap_subject_scores.csv"))
cat("✓ Saved subject scores to: wsap_subject_scores.csv\n")

# Save trial-level data
write_csv(df, file.path(OUTPUT_DIR, "wsap_cleaned_data.csv"))
cat("✓ Saved cleaned trial data to: wsap_cleaned_data.csv\n")

# Save domain-specific scores
write_csv(domain_scores, file.path(OUTPUT_DIR, "wsap_domain_scores.csv"))
cat("✓ Saved domain-specific scores to: wsap_domain_scores.csv\n")
```

---

# Session Information

```{r session-info}
sessionInfo()
```

---

# References

Beard, C., & Amir, N. (2009). Interpretation in social anxiety: When meaning precedes ambiguity. *Cognitive Therapy and Research, 33*(4), 406-415. https://doi.org/10.1007/s10608-009-9235-0

Amir, N., Beard, C., & Bower, E. (2005). Interpretation bias and social anxiety. *Cognitive Therapy and Research, 29*(4), 433-443.

---

**Analysis Complete!** 🎉
