---
title: "Replication of Beard & Amir (2010, Cognitive Therapy and Research)"
author: "Eric Martz (emartz@stanford.edu)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
format:
  html:
    code-fold: true        # Makes code collapsible
    code-tools: true       # Adds show/hide code button
execute:
  echo: false              # Hide all code by default
  warning: false           # Hide all warnings
  message: false           # Hide all messages
---

<!-- Replication reports should all use this template to standardize reporting across projects.  These reports will be public supplementary materials that accompany the summary report(s) of the aggregate results. -->

## Introduction

**Project Proposal**

I chose this study because I am relatively new to psychology research as I pivot from my MS in Computer Science toward preparing for grad school in clinical psychology. As a result, I wanted to replicate an experiment related to clinical psychology, which posed some challenges as there are relatively few studies that are single session and can be administered entirely online. "Interpretation in Social Anxiety: When Meaning Precedes Ambiguity" by Beard & Amir is one of few studies that meet these requirements while also aligning with my research interests in anxiety and depression. The paper explores how interpretation biases change depending on the level of self-reported anxiety individuals have.

The study procedure will begin by asking participants to complete three self-report measures: Social Phobia and Anxiety Inventory (SPAI; Turner et al. 1989), the State Trait Anxiety Inventory (STAI; Spielberger et al. 1970) and the Beck Depression Inventory (BDI; Beck and Steer 1987). They will then complete the Word Sentence Association Paradigm, which asks participants to stare at a fixation cross for 500 ms, read a priming word that is either benign or threat-related for 500 ms, read an ambiguous sentence, then upon finishing reading choose whether the priming word applied to the sentence or not. The reaction times, percentage of benign responses, and percentage of threat responses were measured.

One potential challenge of replication will be that the author only shared five example sentences and prime words, but I intend to reach out to the author to request the full set of word-sentence pairs. Another will be coding the interface used to administer the experiment, since I have never built an experiment before (although I hope my other coding experience will help).

You can find the original paper here: https://pmc.ncbi.nlm.nih.gov/articles/PMC2792932/

You can find my GitHub repository here: https://github.com/psych251/beard2010

---

## Methods

### Power Analysis

<!-- Original effect size, power analysis for samples to achieve 80%, 90%, 95% power to detect that effect size. Considerations of feasibility for selecting planned sample size. -->

In the original paper, the primary between-group comparisons showed large effects (Cohen's d = 0.75–0.94). The below table shows the key effect sizes for each comparison:
```{r include=F}
library(pwr)
n_per_group <- 26
total_analyzed <- 52
total_recruited <- 86
excluded <- 34

cat("Sample Size:\n")
cat("  Total recruited:", total_recruited, "\n")
cat("  Excluded (middle 40% SPIN):", excluded, "\n")
cat("  Final analyzed:", total_analyzed, "(", n_per_group, "per group)\n\n")

# Original effect sizes from Beard & Amir (2009)
effects <- data.frame(
  Effect = c("Threat bias (SA > NAC)",
             "Benign bias (SA > NAC)", 
             "RT reject threat",
             "RT endorse benign"),
  Original_d = c(0.84, 0.75, 0.82, 0.94),
  Original_p = c("< .005", "< .02", ".006", ".002")
)

# Calculate power for each effect with n=26
effects$Power_achieved <- sapply(effects$Original_d, function(d) {
  pwr.t.test(
    n = n_per_group,
    d = d,
    sig.level = 0.05,
    type = "two.sample"
  )$power
})

effects$Power_pct <- paste0(round(effects$Power_achieved * 100, 1), "%")

cat("Table: Statistical Power for Key Comparisons\n\n")
print(knitr::kable(effects[, c("Effect", "Original_d", "Original_p", "Power_pct")],
                   col.names = c("Effect", "Cohen's d", "Original p", "Power"),
                   row.names = FALSE))
```


In order to determine the 80%, 90%, and 95% power to detect these effect sizes, we compute the following: 
```{r include=F}
library(pwr)
library(knitr)

# Effect sizes from original study
d_values <- c(0.75, 0.82, 0.84, 0.94)
effect_names <- c("Benign bias", "RT reject threat", "Threat bias", "RT endorse benign")

# Power levels to test
power_levels <- c(0.80, 0.90, 0.95)

# Create results table
results <- data.frame()

for (i in 1:length(d_values)) {
  for (power in power_levels) {
    pwr_result <- pwr.t.test(
      d = d_values[i],
      sig.level = 0.05,
      power = power,
      type = "two.sample"
    )
    
    n_per_group <- ceiling(pwr_result$n)
    total_analyzed <- n_per_group * 2
    total_recruited <- ceiling(total_analyzed / 0.54)  # Account for 46% exclusion rate
    
    results <- rbind(results, data.frame(
      Effect = effect_names[i],
      d = d_values[i],
      Power = paste0(power * 100, "%"),
      n_per_group = n_per_group,
      Total_analyzed = total_analyzed,
      Total_recruited = total_recruited
    ))
  }
}

kable(results, 
      col.names = c("Effect", "Cohen's d", "Target Power", "n per Group", "Total Analyzed", "Total Recruited*"),
      row.names = FALSE)
```

With our sample size of 26 participants per group (N = 52), we achieve 77–96% power (average 84%) to detect these effects at α = .05, two-tailed. This sample size matches the original study and provides adequate power to detect effects within the observed range.

While power for the benign bias effect (77%) falls slightly below the conventional 80% threshold, this represents only a 3% reduction in detection probability. Given that: (1) the original study found this effect significant with identical sample size, (2) our average power across all key comparisons was 84%, (3) our primary hypothesis concerns threat bias (84% power) and (4) class budgetary restrictions prevent me from going any higher than this sample size, this  should be appropriate and feasible for my replication purposes.

### Planned Sample

<!-- Planned sample size and/or termination rule, sampling frame, known demographics if any, preselection rules if any. -->

I plan to recruit 86 participants to adhere to the methods reported in the paper which took the bottom 30% and top 30% of participants based on their score on the social anxiety scale. This would mean 26 participants in each group, with the middle 40% excluded. However, I expect the final sample size to be slightly smaller due to attrition from failed attention checks. Due to class budgetary restrictions, I cannot go above this number, so my analysis may be slightly more underpowered than the above estimates. 

I plan to recruit 86 participants through Prolific. The sampling frame will consist of English-speaking adults aged 18 or older. No preselection will be applied based on social anxiety scores; participants will complete the Social Phobia Inventory (SPIN) as part of the study, and group assignment will be determined post-hoc by taking the top 30% (high social anxiety; SA group) and bottom 30% (low social anxiety; NAC group) of SPIN scores, with the middle 40% excluded from analysis. 

### Materials

From the original paper:
"Word Sentence Association Paradigm
We created 76 ambiguous sentences that described social situations (e.g., “People laugh after something you said”) and 34 sentences that described non-social situations (e.g., “Part of the building is blown up”).Footnote2 We selected two words for each ambiguous sentence: one that corresponded to a threat interpretation (e.g., “embarrassing” or “terrorist”) and one that corresponded to a benign interpretation (e.g., “funny” or “construction,” see “Appendix” for more examples). We then divided the word sentence pairs (220 total) into two sets of materials (A and B) to create two versions of the task. Sets were matched with respect to the types of situations depicted in the sentences (e.g., dating, work, performance). Within each set participants saw 55 ambiguous sentences: once paired with the threat interpretation prime (55 trials) and once with the benign interpretation prime (55 trials) for a total of 110 trials. No word–sentence pairs were repeated across sets, and the word–sentence pairs were presented in a different random order to each participant. We randomly assigned participants to each set (Set A: n = 31; Set B: n = 21)."

This procedure was followed precisely using the exact word-sentence pairs used in the original study.

### Procedure

From the original paper:
"Participants were assessed individually. They read and signed a consent form, provided basic demographic information, and completed the self-report measures (i.e., SPAI, STAI, BDI). Participants then completed the WSAP on a computer.

Word Sentence Association Paradigm
Each WSAP trial comprised four steps. First, a fixation cross appeared on the computer screen for 500 ms. The fixation cross directed the participants’ attention toward the middle of the screen and alerted them that a trial was beginning. Second, a prime representing either a threat interpretation (e.g., “embarrassing”) or a benign interpretation (e.g., “funny”) appeared in the center of the computer screen for 500 ms. Third, an ambiguous sentence (e.g., “People laugh after something you said”) appeared and remained on the screen until participants pressed the space bar indicating that they finished reading the sentence. Finally, the computer prompted participants to press ‘#1’ on the number pad if they thought the word and sentence were related or to press ‘#3’ on the number pad if the word and sentence were not related (see Fig. 1). Participants then pressed the space bar, and the next trial began. All text appeared in black, 12 point font against a gray background."

Key differences:
Due to a lack of availability of the Social Phobia and Anxiety Inventory (STAI), I used the Social Phobia Inventory (SPIN) instead. Additionally, at the recommendation of the original author, Courtney Beard, I changed the response keys from 1 and 3 to the left and right arrows to more closely emulate the position and convenience of the number pad. 

### Analysis Plan

<!-- Can also quote directly, though it is less often spelled out effectively for an analysis strategy section. The key is to report an analysis strategy that is as close to the original - data cleaning rules, data exclusion rules, covariates, etc. - as possible. -->

Following the original study, participants who scored in the middle 40% of social anxiety scores will be excluded. Reaction times will be excluded on a trial-by-trial basis if they fall below 50 ms or above 2000 ms. 

In addition to these exclusions, I chose to add three attention checks to my trials. I will exclude participants who do not pass at least two of the three checks. Note that these were added after my Pilot B data was processed.

The key analyses I will conduct are 

1) a 2 (Group: SA, NAC) × 2 (Valence) × 2 (Response type) × 2 (Sentence type) mixed ANOVA on reaction times, with follow-up ANOVAs for social vs. non-social sentences if the four-way interaction is significant; 

(2) a 2 (Group) × 2 (Valence) × 2 (Sentence type) mixed ANOVA on endorsement rates; and 

(3) independent-samples t-tests comparing bias scores between groups.


### Differences from Original Study

<!-- Explicitly describe known differences in sample, setting, procedure, and analysis plan from original study. The goal, of course, is to minimize those differences, but differences will inevitably occur. Also, note whether such differences are anticipated to make a difference based on claims in the original article or subsequent published research on the conditions for obtaining the effect. -->

The most significant deviation from the original study is the different social anxiety inventory used. Due to a lack of public access for the Social Phobia and Anxiety Inventory (STAI), I used the Social Phobia Inventory (SPIN) instead. Additionally, the experiment is conducted over Prolific rather than in person as in the original study. Attention checks were added during the WSAP task to exclude participants who failed 2 or more of the checks. As a result, the sample may be slightly smaller, since while the same sample was recruited, this likely will decrease in size once participants who failed the attention checks are excluded. Lastly, after my Pilot B was completed, I received guidance from the original author to change the response keys from 1 and 3 to the left and right arrows for ease of use. I do not expect any of these changes to significantly affect the outcome of the study, except for being more underpowered if the sample size is substantially smaller. 

<!-- ### Methods Addendum (Post Data Collection) -->

<!-- You can comment this section out prior to final report with data collection. -->

#### Actual Sample

<!-- Sample size, demographics, data exclusions based on rules spelled out in analysis plan -->

The Pilot B study consisted of 6 participants, with 2 being assigned the lower SA group, 2 being assigned the higher SA group, and 2 being excluded. Of the four participants included, 50% were female, and ranged in age from 18-24 to 55-64 age groups. 

#### Differences from pre-data collection methods plan

<!-- Any differences from what was described as the original plan, or “none”. -->

After Pilot B, I decided to change the response keys from 1 and 3 to left and right arrows. I also added attention checks. Otherwise, my methods remained the same. 

## Results

### Data preparation

Data preparation following the analysis plan.

```{r}
### Data Preparation

#### Load Relevant Libraries and Functions
library(tidyverse)
library(ez)
library(lsr)
library(knitr)
library(kableExtra)

# Configuration Settings
DATA_FOLDER <- "../../pilot_b_data" # Folder with participant CSV files, normally "../data/"
WSAP_REFERENCE <- "../paradigm/WSAP.csv"        # Reference file with word-sentence pairs

# RT CLEANING (per paper)
RT_MIN <- 50                        # Minimum RT in ms
RT_MAX <- 2000                      # Maximum RT in ms


#### Import data
# Load WSAP reference file
wsap_reference <- read_csv(WSAP_REFERENCE, show_col_types = FALSE) %>%
  rename(
    set = Test,
    valence = `Trial type`,
    word = Word,
    sentence = Sentence,
    domain = Domain
  ) %>%
  mutate(
    valence = tolower(valence),
    valence = if_else(valence == "negative", "threat", "benign"),
    sentence_type = case_when(
      domain == "sad" ~ "social",
      domain == "gad" ~ "non_social",
      TRUE ~ NA_character_
    ),
    word = str_trim(word),
    sentence = str_trim(sentence)
  ) %>%
  select(set, word, sentence, valence, sentence_type)

# Load participant data
csv_files <- list.files(DATA_FOLDER, pattern = "\\.csv$", full.names = TRUE)
df_list <- lapply(csv_files, function(file) {
  df <- read_csv(file, show_col_types = FALSE, col_types = cols(.default = "c"))
  if (!"subject" %in% names(df)) {
    df$subject <- tools::file_path_sans_ext(basename(file))
  }
  return(df)
})

raw_data <- bind_rows(df_list)


raw_data <- raw_data %>%
  mutate(
    across(c(spin_total, stai_state_total, stai_trait_total, 
             bdi_total, trial_index, time_elapsed), 
           ~suppressWarnings(as.numeric(.))),
    across(c(word, sentence, domain, response_key, subject, trial_part), 
           as.character)
  )
raw_data <- raw_data %>%
  group_by(subject) %>%
  fill(age, gender, race_ethnicity, education, native_english, 
       .direction = "down") %>%
  ungroup()

#### Data exclusion / filtering
# Clean WSAP trials
wsap_clean <- raw_data %>%
  filter(task == "wsap") %>%  # Only judgment trials
  mutate(
    word = str_trim(word),
    sentence = str_trim(sentence),
    # Extract judgment RT from rt column
    judgment_rt_clean = as.numeric(rt)
  ) %>%
  left_join(
    wsap_reference %>% select(word, sentence, valence, sentence_type),
    by = c("word", "sentence")
  ) %>%
  mutate(
    response_type = case_when(
      response_key == "1" ~ "endorsement",
      response_key == "3" ~ "rejection",
      TRUE ~ NA_character_
    ),
    endorsed = if_else(response_key == "1", 1, 0),
    # Apply RT cleaning based on paper criteria
    rt_clean = case_when(
      judgment_rt_clean >= RT_MIN & judgment_rt_clean <= RT_MAX ~ judgment_rt_clean,
      TRUE ~ NA_real_
    )
  ) %>%
  filter(!is.na(valence), !is.na(sentence_type), !is.na(response_type)) %>%
  select(subject, trial_index, word, sentence, domain, valence, sentence_type,
         response_type, endorsed, 
         judgment_rt = judgment_rt_clean,
         rt_clean)

# Exclude participants with incomplete data
valid_subjects <- wsap_clean %>%
  group_by(subject) %>%
  summarise(n_trials = n(), .groups = "drop") %>%
  filter(n_trials >= 50) %>%
  pull(subject)

wsap_clean <- wsap_clean %>%
  filter(subject %in% valid_subjects)

# Attention check exclusions (not run for Pilot B, to be added)
# attention_summary <- raw_data %>%
#   filter(task == "attention_check") %>%
#   group_by(subject) %>%
#   summarise(
#     attention_passed = sum(passed == TRUE, na.rm = TRUE),
#     attention_total = n(),
#     attention_rate = attention_passed / attention_total,
#     .groups = "drop"
#   )
# 
# failed_attention <- attention_summary %>%
#   filter(attention_passed < 2) %>%
#   pull(subject)
# 
# valid_subjects <- setdiff(valid_subjects, failed_attention)

wsap_clean <- wsap_clean %>%
  filter(subject %in% valid_subjects)

#### Prepare data for analysis - create columns etc.
# Extract participant-level info
#### Prepare data for analysis - create columns etc.
# Extract participant-level info
participant_info <- raw_data %>%
  group_by(subject) %>%
  summarise(
    set_assigned = first(na.omit(set_assigned)),
    spin_total = first(na.omit(spin_total)),
    stai_state_total = first(na.omit(stai_state_total)),
    stai_trait_total = first(na.omit(stai_trait_total)),
    bdi_total = first(na.omit(bdi_total)),
    age = first(na.omit(age)),
    gender = first(na.omit(gender)),
    race_ethnicity = first(na.omit(race_ethnicity)),
    education = first(na.omit(education)),
    native_english = first(na.omit(native_english)),
    .groups = "drop"
  ) %>%
  filter(subject %in% valid_subjects)

# Assign groups based on SPIN percentiles
  percentile_30 <- quantile(participant_info$spin_total, 0.30, na.rm = TRUE)
  percentile_70 <- quantile(participant_info$spin_total, 0.70, na.rm = TRUE)
  
  participant_info <- participant_info %>%
    mutate(
      group = case_when(
        spin_total >= percentile_70 ~ "SA",
        spin_total <= percentile_30 ~ "NAC",
        TRUE ~ "exclude"
      )
    )


### Sample Characteristics and Exclusions

#### Sample Size and Exclusions

# Total recruited
n_recruited <- n_distinct(raw_data$subject)

# Exclusions
n_incomplete <- length(setdiff(unique(raw_data$subject), valid_subjects))

# Attention check failures (if applicable)
n_attention_failed <- if(exists("failed_attention")) length(failed_attention) else 0

# Middle 40% excluded based on SPIN
n_middle_excluded <- sum(participant_info$group == "exclude")

# Final sample
n_sa <- sum(participant_info$group == "SA")
n_nac <- sum(participant_info$group == "NAC")
n_analyzed <- n_sa + n_nac

# Create exclusion summary table
exclusion_summary <- data.frame(
  Stage = c("Total recruited",
            "Excluded: Incomplete data",
            "Excluded: Attention checks failed",
            "After quality exclusions",
            "Excluded: Middle 40% SPIN scores",
            "Final analyzed sample",
            "  SA group (high social anxiety)",
            "  NAC group (low social anxiety)"),
  N = c(n_recruited,
        n_incomplete,
        n_attention_failed,
        n_recruited - n_incomplete - n_attention_failed,
        n_middle_excluded,
        n_analyzed,
        n_sa,
        n_nac),
  Percentage = c(100,
                 round(100 * n_incomplete / n_recruited, 1),
                 round(100 * n_attention_failed / n_recruited, 1),
                 round(100 * (n_recruited - n_incomplete - n_attention_failed) / n_recruited, 1),
                 round(100 * n_middle_excluded / (n_recruited - n_incomplete - n_attention_failed), 1),
                 round(100 * n_analyzed / n_recruited, 1),
                 round(100 * n_sa / n_analyzed, 1),
                 round(100 * n_nac / n_analyzed, 1))
)

kable(exclusion_summary,
      caption = "Sample Size and Exclusions",
      col.names = c("Stage", "N", "% of Total"),
      align = c("l", "c", "c")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)


#### Demographics by Group
# Calculate demographics
demo_summary <- participant_info %>%
  filter(group != "exclude") %>%  # Only analyze SA and NAC groups
  group_by(group) %>%
  summarise(
    n = n(),
    # Age distribution
    age_18_24 = sum(age == "18-24", na.rm = TRUE),
    age_25_34 = sum(age == "25-34", na.rm = TRUE),
    age_35_44 = sum(age == "35-44", na.rm = TRUE),
    age_45_54 = sum(age == "45-54", na.rm = TRUE),
    age_55_64 = sum(age == "55-64", na.rm = TRUE),
    age_65_plus = sum(age == "65 or older", na.rm = TRUE),
    # Gender distribution
    female = sum(gender == "Female", na.rm = TRUE),
    male = sum(gender == "Male", na.rm = TRUE),
    nonbinary_other = sum(gender %in% c("Non-binary", "Other"), na.rm = TRUE),
    prefer_not_say = sum(gender == "Prefer not to say", na.rm = TRUE),
    .groups = "drop"
  )

# Convert to percentages
demo_pct <- demo_summary %>%
  mutate(
    across(starts_with("age_"), ~ paste0(.x, " (", round(100 * .x / n, 1), "%)")),
    across(c(female, male, nonbinary_other, prefer_not_say), 
           ~ paste0(.x, " (", round(100 * .x / n, 1), "%)"))
  ) %>%
  select(-n)

# Transpose for better display
demo_table <- data.frame(
  Characteristic = c("Age: 18-24", "Age: 25-34", "Age: 35-44", "Age: 45-54", "Age: 55-64", "Age: 65+","Gender: Female", "Gender: Male", "Gender: Non-binary/Other", 
                     "Gender: Prefer not to say"),
  SA = c(demo_pct$age_18_24[demo_pct$group == "SA"],
         demo_pct$age_25_34[demo_pct$group == "SA"],
         demo_pct$age_35_44[demo_pct$group == "SA"],
         demo_pct$age_45_54[demo_pct$group == "SA"],
         demo_pct$age_55_64[demo_pct$group == "SA"],
         demo_pct$age_65_plus[demo_pct$group == "SA"],
         demo_pct$female[demo_pct$group == "SA"],
         demo_pct$male[demo_pct$group == "SA"],
         demo_pct$nonbinary_other[demo_pct$group == "SA"],
         demo_pct$prefer_not_say[demo_pct$group == "SA"]),
  NAC = c(demo_pct$age_18_24[demo_pct$group == "NAC"],
          demo_pct$age_25_34[demo_pct$group == "NAC"],
          demo_pct$age_35_44[demo_pct$group == "NAC"],
          demo_pct$age_45_54[demo_pct$group == "NAC"],
         demo_pct$age_55_64[demo_pct$group == "NAC"],
         demo_pct$age_65_plus[demo_pct$group == "NAC"],
          demo_pct$female[demo_pct$group == "NAC"],
          demo_pct$male[demo_pct$group == "NAC"],
          demo_pct$nonbinary_other[demo_pct$group == "NAC"],
          demo_pct$prefer_not_say[demo_pct$group == "NAC"])
)

kable(demo_table,
      caption = "Demographics by Group",
      col.names = c("Characteristic", paste0("SA (n = ", n_sa, ")"), 
                    paste0("NAC (n = ", n_nac, ")")),
      align = c("l", "c", "c")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
  pack_rows("Age Distribution", 1, 6) %>%
  pack_rows("Gender Distribution", 7, 10)
```

### Confirmatory analysis

The analyses as specified in the analysis plan.
```{r}
# Calculate endorsement rates
endorsement_rates <- wsap_clean %>%
  group_by(subject, sentence_type, valence) %>%
  summarise(
    pct_endorsed = mean(endorsed, na.rm = TRUE) * 100,
    n_trials = n(),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from = c(sentence_type, valence),
    values_from = pct_endorsed,
    names_prefix = "pct_"
  )

# Calculate reaction times
rt_means <- wsap_clean %>%
  filter(!is.na(rt_clean)) %>%
  group_by(subject, sentence_type, valence, response_type) %>%
  summarise(
    mean_rt = mean(rt_clean, na.rm = TRUE),
    n_trials = n(),
    .groups = "drop"
  ) %>%
  select(-n_trials) %>%  # KEY FIX: Remove n_trials before pivoting
  pivot_wider(
    names_from = c(sentence_type, valence, response_type),
    values_from = mean_rt,
    names_prefix = "rt_"
  )

# Calculate bias scores
bias_scores <- rt_means %>%
  mutate(
    # Threat bias = RT(reject threat) - RT(endorse threat)
    threat_bias_social = rt_social_threat_rejection - rt_social_threat_endorsement,
    benign_bias_social = rt_social_benign_endorsement - rt_social_benign_rejection,
    
    threat_bias_nonsocial = rt_non_social_threat_rejection - rt_non_social_threat_endorsement,
    benign_bias_nonsocial = rt_non_social_benign_endorsement - rt_non_social_benign_rejection
  ) %>%
  select(subject, contains("bias"))

# Combine all participant data
participant_data <- participant_info %>%
  left_join(endorsement_rates, by = "subject") %>%
  left_join(rt_means, by = "subject") %>%
  left_join(bias_scores, by = "subject")

# Filter to analysis groups only
analysis_data <- participant_data %>%
  filter(group %in% c("SA", "NAC"))

# Prepare long format for ANOVAs
anova_data_long <- wsap_clean %>%
  left_join(participant_info %>% select(subject, group, spin_total), by = "subject") %>%
  filter(group %in% c("SA", "NAC")) %>%
  select(subject, group, spin_total, sentence_type, valence, 
         response_type, rt_clean, endorsed, trial_index) %>%
  mutate(
    group = factor(group, levels = c("NAC", "SA")),
    sentence_type = factor(sentence_type, levels = c("social", "non_social")),
    valence = factor(valence, levels = c("benign", "threat")),
    response_type = factor(response_type, levels = c("endorsement", "rejection"))
  )
#### Primary Mixed ANOVA: Reaction Times
# Group × Valence × Response Type × Sentence Type
anova_rt <- ezANOVA(
  data = anova_data_long %>% filter(!is.na(rt_clean)),
  dv = rt_clean,
  wid = subject,
  within = .(valence, response_type, sentence_type),
  between = group,
  type = 3,
  detailed = TRUE
)

# kable(anova_rt$ANOVA, 
#       caption = "Mixed ANOVA: Reaction Times",
#       digits = 3)

#### Follow-up ANOVA: Social Sentences Only
# Group × Valence × Response Type for social sentences
anova_rt_social <- ezANOVA(
  data = anova_data_long %>% filter(!is.na(rt_clean), sentence_type == "social"),
  dv = rt_clean,
  wid = subject,
  within = .(valence, response_type),
  between = group,
  type = 3,
  detailed = TRUE
)

# kable(anova_rt_social$ANOVA,
#       caption = "Mixed ANOVA: Reaction Times (Social Sentences Only)",
#       digits = 3)

#### Independent t-tests: Bias Scores
# Threat bias
threat_bias_test <- t.test(threat_bias_social ~ group, data = analysis_data)
threat_bias_d <- cohensD(threat_bias_social ~ group, data = analysis_data)

# Benign bias
benign_bias_test <- t.test(benign_bias_social ~ group, data = analysis_data)
benign_bias_d <- cohensD(benign_bias_social ~ group, data = analysis_data)

```

```{r}
### Descriptive Statistics: Original vs Replication

# Original study values (from Table 2)
original_descriptives <- data.frame(
  Measure = c(
    # Self-report indices
    "Social threat endorsement (%)",
    "Social benign endorsement (%)",
    "Non-social threat endorsement (%)",
    "Non-social benign endorsement (%)",
    # Social sentences RT
    "RT: Endorse threat (social)",
    "RT: Endorse benign (social)",
    "RT: Reject threat (social)",
    "RT: Reject benign (social)",
    "Threat bias score (social)",
    "Benign bias score (social)",
    # Non-social sentences RT
    "RT: Endorse threat (non-social)",
    "RT: Endorse benign (non-social)",
    "RT: Reject threat (non-social)",
    "RT: Reject benign (non-social)"
  ),
  Original_SA_M = c(59, 52, 59, 64, 532, 657, 626, 577, 94, 80, 550, 538, 571, 662),
  Original_SA_SD = c(18, 19, 18, 15, 163, 226, 267, 200, 203, 181, 183, 183, 187, 286),
  Original_NAC_M = c(30, 71, 49, 71, 485, 460, 447, 507, -39, -47, 434, 477, 470, 513),
  Original_NAC_SD = c(18, 14, 23, 18, 186, 199, 169, 228, 101, 166, 121, 198, 198, 235)
)

# Calculate replication values
replication_descriptives <- data.frame(
  Measure = c(
    # Self-report indices
    "Social threat endorsement (%)",
    "Social benign endorsement (%)",
    "Non-social threat endorsement (%)",
    "Non-social benign endorsement (%)",
    # Social sentences RT
    "RT: Endorse threat (social)",
    "RT: Endorse benign (social)",
    "RT: Reject threat (social)",
    "RT: Reject benign (social)",
    "Threat bias score (social)",
    "Benign bias score (social)",
    # Non-social sentences RT
    "RT: Endorse threat (non-social)",
    "RT: Endorse benign (non-social)",
    "RT: Reject threat (non-social)",
    "RT: Reject benign (non-social)"
  ),
  Replication_SA_M = c(
    mean(analysis_data$pct_social_threat[analysis_data$group == "SA"], na.rm = TRUE),
    mean(analysis_data$pct_social_benign[analysis_data$group == "SA"], na.rm = TRUE),
    mean(analysis_data$pct_non_social_threat[analysis_data$group == "SA"], na.rm = TRUE),
    mean(analysis_data$pct_non_social_benign[analysis_data$group == "SA"], na.rm = TRUE),
    mean(analysis_data$rt_social_threat_endorsement[analysis_data$group == "SA"], na.rm = TRUE),
    mean(analysis_data$rt_social_benign_endorsement[analysis_data$group == "SA"], na.rm = TRUE),
    mean(analysis_data$rt_social_threat_rejection[analysis_data$group == "SA"], na.rm = TRUE),
    mean(analysis_data$rt_social_benign_rejection[analysis_data$group == "SA"], na.rm = TRUE),
    mean(analysis_data$threat_bias_social[analysis_data$group == "SA"], na.rm = TRUE),
    mean(analysis_data$benign_bias_social[analysis_data$group == "SA"], na.rm = TRUE),
    mean(analysis_data$rt_non_social_threat_endorsement[analysis_data$group == "SA"], na.rm = TRUE),
    mean(analysis_data$rt_non_social_benign_endorsement[analysis_data$group == "SA"], na.rm = TRUE),
    mean(analysis_data$rt_non_social_threat_rejection[analysis_data$group == "SA"], na.rm = TRUE),
    mean(analysis_data$rt_non_social_benign_rejection[analysis_data$group == "SA"], na.rm = TRUE)
  ),
  Replication_SA_SD = c(
    sd(analysis_data$pct_social_threat[analysis_data$group == "SA"], na.rm = TRUE),
    sd(analysis_data$pct_social_benign[analysis_data$group == "SA"], na.rm = TRUE),
    sd(analysis_data$pct_non_social_threat[analysis_data$group == "SA"], na.rm = TRUE),
    sd(analysis_data$pct_non_social_benign[analysis_data$group == "SA"], na.rm = TRUE),
    sd(analysis_data$rt_social_threat_endorsement[analysis_data$group == "SA"], na.rm = TRUE),
    sd(analysis_data$rt_social_benign_endorsement[analysis_data$group == "SA"], na.rm = TRUE),
    sd(analysis_data$rt_social_threat_rejection[analysis_data$group == "SA"], na.rm = TRUE),
    sd(analysis_data$rt_social_benign_rejection[analysis_data$group == "SA"], na.rm = TRUE),
    sd(analysis_data$threat_bias_social[analysis_data$group == "SA"], na.rm = TRUE),
    sd(analysis_data$benign_bias_social[analysis_data$group == "SA"], na.rm = TRUE),
    sd(analysis_data$rt_non_social_threat_endorsement[analysis_data$group == "SA"], na.rm = TRUE),
    sd(analysis_data$rt_non_social_benign_endorsement[analysis_data$group == "SA"], na.rm = TRUE),
    sd(analysis_data$rt_non_social_threat_rejection[analysis_data$group == "SA"], na.rm = TRUE),
    sd(analysis_data$rt_non_social_benign_rejection[analysis_data$group == "SA"], na.rm = TRUE)
  ),
  Replication_NAC_M = c(
    mean(analysis_data$pct_social_threat[analysis_data$group == "NAC"], na.rm = TRUE),
    mean(analysis_data$pct_social_benign[analysis_data$group == "NAC"], na.rm = TRUE),
    mean(analysis_data$pct_non_social_threat[analysis_data$group == "NAC"], na.rm = TRUE),
    mean(analysis_data$pct_non_social_benign[analysis_data$group == "NAC"], na.rm = TRUE),
    mean(analysis_data$rt_social_threat_endorsement[analysis_data$group == "NAC"], na.rm = TRUE),
    mean(analysis_data$rt_social_benign_endorsement[analysis_data$group == "NAC"], na.rm = TRUE),
    mean(analysis_data$rt_social_threat_rejection[analysis_data$group == "NAC"], na.rm = TRUE),
    mean(analysis_data$rt_social_benign_rejection[analysis_data$group == "NAC"], na.rm = TRUE),
    mean(analysis_data$threat_bias_social[analysis_data$group == "NAC"], na.rm = TRUE),
    mean(analysis_data$benign_bias_social[analysis_data$group == "NAC"], na.rm = TRUE),
    mean(analysis_data$rt_non_social_threat_endorsement[analysis_data$group == "NAC"], na.rm = TRUE),
    mean(analysis_data$rt_non_social_benign_endorsement[analysis_data$group == "NAC"], na.rm = TRUE),
    mean(analysis_data$rt_non_social_threat_rejection[analysis_data$group == "NAC"], na.rm = TRUE),
    mean(analysis_data$rt_non_social_benign_rejection[analysis_data$group == "NAC"], na.rm = TRUE)
  ),
  Replication_NAC_SD = c(
    sd(analysis_data$pct_social_threat[analysis_data$group == "NAC"], na.rm = TRUE),
    sd(analysis_data$pct_social_benign[analysis_data$group == "NAC"], na.rm = TRUE),
    sd(analysis_data$pct_non_social_threat[analysis_data$group == "NAC"], na.rm = TRUE),
    sd(analysis_data$pct_non_social_benign[analysis_data$group == "NAC"], na.rm = TRUE),
    sd(analysis_data$rt_social_threat_endorsement[analysis_data$group == "NAC"], na.rm = TRUE),
    sd(analysis_data$rt_social_benign_endorsement[analysis_data$group == "NAC"], na.rm = TRUE),
    sd(analysis_data$rt_social_threat_rejection[analysis_data$group == "NAC"], na.rm = TRUE),
    sd(analysis_data$rt_social_benign_rejection[analysis_data$group == "NAC"], na.rm = TRUE),
    sd(analysis_data$threat_bias_social[analysis_data$group == "NAC"], na.rm = TRUE),
    sd(analysis_data$benign_bias_social[analysis_data$group == "NAC"], na.rm = TRUE),
    sd(analysis_data$rt_non_social_threat_endorsement[analysis_data$group == "NAC"], na.rm = TRUE),
    sd(analysis_data$rt_non_social_benign_endorsement[analysis_data$group == "NAC"], na.rm = TRUE),
    sd(analysis_data$rt_non_social_threat_rejection[analysis_data$group == "NAC"], na.rm = TRUE),
    sd(analysis_data$rt_non_social_benign_rejection[analysis_data$group == "NAC"], na.rm = TRUE)
  )
)

# Combine tables
combined_descriptives <- original_descriptives %>%
  left_join(replication_descriptives, by = "Measure") %>%
  mutate(
    Original_SA = sprintf("%.0f (%.0f)", Original_SA_M, Original_SA_SD),
    Original_NAC = sprintf("%.0f (%.0f)", Original_NAC_M, Original_NAC_SD),
    Replication_SA = sprintf("%.0f (%.0f)", Replication_SA_M, Replication_SA_SD),
    Replication_NAC = sprintf("%.0f (%.0f)", Replication_NAC_M, Replication_NAC_SD)
  ) %>%
  select(Measure, Original_SA, Original_NAC, Replication_SA, Replication_NAC)

kable(combined_descriptives,
      caption = "Table 1: Descriptive Statistics - Original vs Replication",
      col.names = c("Measure", "Original SA\nM (SD)", "Original NAC\nM (SD)", 
                    "Replication SA\nM (SD)", "Replication NAC\nM (SD)"),
      align = c("l", "c", "c", "c", "c")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
  pack_rows("Self-Report Indices (%)", 1, 4) %>%
  pack_rows("Reaction Time: Social Sentences (ms)", 5, 10) %>%
  pack_rows("Reaction Time: Non-Social Sentences (ms)", 11, 14)

### Key Statistical Effects: Original vs Replication

# Run the key tests for replication
threat_bias_test <- t.test(threat_bias_social ~ group, data = analysis_data)
benign_bias_test <- t.test(benign_bias_social ~ group, data = analysis_data)
threat_endorse_test <- t.test(pct_social_threat ~ group, data = analysis_data)
benign_endorse_test <- t.test(pct_social_benign ~ group, data = analysis_data)

# SA within-group: threat vs benign endorsement
sa_within <- t.test(analysis_data$pct_social_threat[analysis_data$group == "SA"],
                    analysis_data$pct_social_benign[analysis_data$group == "SA"],
                    paired = TRUE)

# NAC within-group: threat vs benign endorsement
nac_within <- t.test(analysis_data$pct_social_threat[analysis_data$group == "NAC"],
                     analysis_data$pct_social_benign[analysis_data$group == "NAC"],
                     paired = TRUE)

# Create comparison table
effects_comparison <- data.frame(
  Effect = c(
    "Threat bias: SA > NAC",
    "Benign bias: SA > NAC",
    "Threat endorsement: SA > NAC",
    "Benign endorsement: NAC > SA",
    "SA: Threat vs Benign endorsement",
    "NAC: Benign > Threat endorsement"
  ),
  Original_Statistic = c("t(50) = 2.98", "t(50) = 2.64", "F(1,50) = 34.26", 
                         "F(1,50) = 16.64", "t(25) = 1.39", "t(25) = -10.56"),
  Original_p = c("< .005", "< .02", "< .001", "< .001", ".16", "< .001"),
  Original_sig = c("***", "*", "***", "***", "ns", "***"),
  Replication_Statistic = c(
    sprintf("t(%.0f) = %.2f", threat_bias_test$parameter, threat_bias_test$statistic),
    sprintf("t(%.0f) = %.2f", benign_bias_test$parameter, benign_bias_test$statistic),
    sprintf("t(%.0f) = %.2f", threat_endorse_test$parameter, threat_endorse_test$statistic),
    sprintf("t(%.0f) = %.2f", benign_endorse_test$parameter, benign_endorse_test$statistic),
    sprintf("t(%.0f) = %.2f", sa_within$parameter, sa_within$statistic),
    sprintf("t(%.0f) = %.2f", nac_within$parameter, nac_within$statistic)
  ),
  Replication_p = c(
    format.pval(threat_bias_test$p.value, digits = 3),
    format.pval(benign_bias_test$p.value, digits = 3),
    format.pval(threat_endorse_test$p.value, digits = 3),
    format.pval(benign_endorse_test$p.value, digits = 3),
    format.pval(sa_within$p.value, digits = 3),
    format.pval(nac_within$p.value, digits = 3)
  ),
  Replication_sig = c(
    ifelse(threat_bias_test$p.value < 0.001, "***",
           ifelse(threat_bias_test$p.value < 0.01, "**",
                  ifelse(threat_bias_test$p.value < 0.05, "*", "ns"))),
    ifelse(benign_bias_test$p.value < 0.001, "***",
           ifelse(benign_bias_test$p.value < 0.01, "**",
                  ifelse(benign_bias_test$p.value < 0.05, "*", "ns"))),
    ifelse(threat_endorse_test$p.value < 0.001, "***",
           ifelse(threat_endorse_test$p.value < 0.01, "**",
                  ifelse(threat_endorse_test$p.value < 0.05, "*", "ns"))),
    ifelse(benign_endorse_test$p.value < 0.001, "***",
           ifelse(benign_endorse_test$p.value < 0.01, "**",
                  ifelse(benign_endorse_test$p.value < 0.05, "*", "ns"))),
    ifelse(sa_within$p.value < 0.001, "***",
           ifelse(sa_within$p.value < 0.01, "**",
                  ifelse(sa_within$p.value < 0.05, "*", "ns"))),
    ifelse(nac_within$p.value < 0.001, "***",
           ifelse(nac_within$p.value < 0.01, "**",
                  ifelse(nac_within$p.value < 0.05, "*", "ns")))
  ),
  Replicated = c(
    ifelse(threat_bias_test$p.value < 0.05 & threat_bias_test$statistic > 0, "Yes", "No"),
    ifelse(benign_bias_test$p.value < 0.05 & benign_bias_test$statistic > 0, "Yes", "No"),
    ifelse(threat_endorse_test$p.value < 0.05 & threat_endorse_test$statistic > 0, "Yes", "No"),
    ifelse(benign_endorse_test$p.value < 0.05 & benign_endorse_test$statistic < 0, "Yes", "No"),
    ifelse(sa_within$p.value >= 0.05, "Yes", "Partial"),  # Original was ns
    ifelse(nac_within$p.value < 0.05 & nac_within$statistic < 0, "Yes", "No")
  )
)

kable(effects_comparison,
      caption = "Table 2: Key Statistical Effects - Original vs Replication",
      col.names = c("Effect", "Original Test", "p", "Sig", 
                    "Replication Test", "p", "Sig", "Replicated?"),
      align = c("l", "c", "c", "c", "c", "c", "c", "c")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
  add_footnote(c("* p < .05, ** p < .01, *** p < .001, ns = not significant",
                 "Note: Pilot B data with n=2 per group - results not interpretable"),
               notation = "none")
```

### Exploratory analyses

Any follow-up analyses desired (not required).

## Discussion

### Summary of Replication Attempt

<!-- Open the discussion section with a paragraph summarizing the primary result from the confirmatory analysis and the assessment of whether it replicated, partially replicated, or failed to replicate the original result. -->

To be completed when full data is collected. 

### Commentary

Add open-ended commentary (if any) reflecting (a) insights from follow-up exploratory analysis, (b) assessment of the meaning of the replication (or not) - e.g., for a failure to replicate, are the differences between original and present study ones that definitely, plausibly, or are unlikely to have been moderators of the result, and (c) discussion of any objections or challenges raised by the current and original authors about the replication attempt. None of these need to be long.
